---  
    title: "Network Analysis"  
    author: "Evan YF W."  
    date: "`r format(Sys.Date())`"
    output: github_document
---  

```{r include=FALSE}
library(igraph)
setwd("/Users/wangevan/Google Drive/UMN MSBA/Spring 2018/Simulation/DataFiles (2)")

gamers <-  read.csv("gamers.csv")
gamers_age <-  read.csv("gamers-age.csv")
```


# Use  the  file gamers.csv to  compute  the  betweenness  centrality  of  the  different vertices.  
```{r}
g <- graph_from_data_frame(gamers,
                           directed = FALSE)
plot(g)

betweenness(g)
```
# Then  use  edge  betweenness algorithm  for  community  detection  and  plot  the  resulting network 
# graph showing the different communities. 

# The size of the vertices in your plot should be proportional to their betweenness centrality score.
```{r}
ebc <- edge.betweenness.community(g)
plot(ebc,
     g,
     vertex.size = (betweenness(g)^0.65)+1)
```


# Use the Forrest Gump dataset in the file ForestGump.csv, make a plot of the ego graph for Lieutenant Dan Taylor 

# (vertex name "LT DAN" in the data set) of order 1 (i.e., one hop) and compute the edge density of the resulting ego graph.
```{r include=FALSE}
fg <-  read.csv("ForestGump.csv")
```

```{r }
g2 <- graph.edgelist(as.matrix(fg),directed = FALSE)

g3 <- make_ego_graph(g2,1,"LT DAN",mode = c("all"))

plot(g3[[1]])
```

# Question 3
# Use  the  file club.csv to  compute  the  average  path  length  for  the  network  graph. 
```{r }
club <- read.csv("club.csv")
```

```{r }
g3 <- graph_from_data_frame(club,directed =  FALSE)

mean_distance(g3)
```


# Create  1000  random  graphs  with  the  same  number  of  vertices  and  similar  edge  density. 
```{r}
g_list <- vector("list",1000)

for(i in 1:1000){
  g_list[[i]] <- erdos.renyi.game(n = gorder(g3), 
                              p.or.m = edge_density(g3), 
                              type = "gnp")
}
```


# Plot  a histogram to show the distribution of the average path lengths in these random graphs and 
```{r}
g3.apls <- unlist(lapply(g_list, mean_distance, directed =  FALSE))

hist(g3.apls,xlim = range(c(2,7)) , breaks = 20)

abline(v = mean_distance(g3), col = "red", lty = 3, lwd = 2)
```


# Calculate the proportion of graphs with an Average Path Length smaller than our 
# Forrest Gump network
```{r}
sum(g3.apls < mean_distance(g3, directed = FALSE))/1000
```

